Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-15 paper/manuscript.Rmd
Compute standardized effect for spatial model

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
\@ref(tab:aov)), meaning that the eveness of biomass across species
temporally increased when the community biomass temporally decreased and
respectively that the evenness temporally decreased when the community biomass
temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We observed the
same pattern between the temporal trends of
community biomass and that of the pielou of individual number.

@@

HERE
The temporal trends of community biomass, average trophic level, pielou of biomass,
pielou of individual had a positive relationship with that of species richness
(Fig. \@ref(fig:rich), Table \@ref(tab:aov)). However, the direct
relationship between the temporal trends of average trophic level and the one of
species richness was not significant after controling for community biomass temporal
trends [**TO CHECK: refaire tous les modèles temporels en mettant à la fois la
pente des biomasses et de la richness en même temps??**].

We also found that the relationship between the temporal trends of pielou of
individual and connectance and that of species richness was dependant of the
overall species richness of the community (Fig. \@ref(fig:rich), Table
\@ref(tab:aov)), meaning that the relationship between temporal trends of
pielou of individual and that of species richness was more positive as the
community contained more species (Fig. \@ref(fig:rich), Table
\@ref(tab:reg)). While the relationship between temporal trends of pielou
of individual and that of species richness was more negative as the community
contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).

>>>>

We found a significant negative relationship between the temporal trends of
community biomass and that of the pielou of biomass (Figure \@ref(fig:bm), Table
\@ref(tab:aov)), meaning that the eveness of biomass across species
temporally increased when the community biomass temporally decreased and
respectively that the evenness of biomass temporally decreased when the community biomass
temporally increased (Fig. \@ref(fig:bm), Table \@ref(tab:aov)). We also found the
same pattern between the temporal trends of community biomass and that of the
pielou of individual number.

@@

The temporal trends of community biomass and pielou of biomass, had a positive
relationship with that of species richness (Fig. \@ref(fig:rich), Table
\@ref(tab:aov)) while we did not find significant relationships between the
temporal trends of average trophic level, connectance, pielou of individual
number and the one of species richness (Fig. \@ref(fig:rich), Table
\@ref(tab:aov)).

---
#We also found that the relationship between the temporal trends of pielou of
#individual and connectance and that of species richness was dependant of the
#overall species richness of the community (Fig. \@ref(fig:rich), Table
#\@ref(tab:aov)), meaning that the relationship between temporal trends of
#pielou of individual and that of species richness was more positive as the
#community contained more species (Fig. \@ref(fig:rich), Table
#\@ref(tab:reg)). While the relationship between temporal trends of pielou
#of individual and that of species richness was more negative as the community
#contained more species (Fig. \@ref(fig:rich), Table \@ref(tab:reg)).
---
